---
title: "sesameData User Guide"
shorttitle: "sesameData guide"
package: sesameData
output: rmarkdown::html_vignette
fig_width: 8
fig_height: 6
vignette: >
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteIndexEntry{sesameData User Guide}
    %\VignetteEncoding{UTF-8}
---

# Installation

From Bioconductor
```{r, eval=FALSE}
if (!requireNamespace("BiocManager", quietly=TRUE))
    install.packages("BiocManager")
BiocManager::install("sesameData")
```

Development version can be installed from github
```{r, eval=FALSE}
library(devtools)
install_github('zwdzwd/sesameData')
```

# Usage

`sesameData` package provides associated data for sesame package. It also 
maintains probe annotation for different Infinium platforms.

Each datum is accessible through the `sesameDataGet` interface which allows
package level in-memory caching. For example, data can be retrieved with the
title: 
```{r}
library(sesameData)
EPIC.hg38.manifest = sesameDataGet('EPIC.hg38.manifest')
```

Titles of all the available data can be shown with:
```{r}
sesameDataList()
```


